---
title: "606 Assignment1 - Loading Data into a Data Frame"
author: "Rajwant Mishra"
date: "January 31, 2019"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Problem Statement 

---

<b >Your task </b>  

+ study the dataset and the associated description of the data (i.e. "data dictionary"). You may need
to look around a bit, but it's there! 

+ You should take the data, and create a data frame with a subset of the columns
in the dataset. 

+ You should include the column that indicates edible or poisonous and three or four other columns.
+ You should also add meaningful column names and replace the abbreviations used in the data-for example, in the appropriate column, "e" might become "edible." 

+ Your deliverable is the R code to perform these transformation tasks.
---

#  Solution {.tabset .tabset-fade .tabset-pills}




## Data Source

+ [Source of Data](https://archive.ics.uci.edu/ml/datasets/mushroom)

+ [Data File](https://archive.ics.uci.edu/ml/machine-learning-databases/mushroom/)

+ [Data Desc] (https://archive.ics.uci.edu/ml/machine-learning-databases/mushroom/agaricus-lepiota.names)

## About DataSet

    (a) Mushroom records drawn from The Audubon Society Field Guide to North
        American Mushrooms (1981). G. H. Lincoff (Pres.), New York: Alfred
        A. Knopf
    (b) Donor: Jeff Schlimmer (Jeffrey.Schlimmer@a.gp.cs.cmu.edu)
    (c) Date: 27 April 1987


## Packages Used
<list>
<li> Tidyverse
<li>stringr
<li>xml
<li>data.table
</list>


## Loading Packages 
~~~~~~~

suppressWarnings(library(tidyverse))
suppressWarnings(library(stringr))
suppressWarnings(library(data.table))
library(plyr)
library(XML)
library(crayon)
library(lubridate)
library(rjson)
library(readxl)

~~~~~~~

```{r include=FALSE}

#install.packages("tidyverse")

suppressWarnings(library(tidyverse))
suppressWarnings(library(stringr))
suppressWarnings(library(data.table))
library(plyr)
library(XML)
library(crayon)
library(lubridate)
library(rjson)
library(readxl) 


```



```{r}

setwd("C:\\Users\\951250\\Documents\\myR\\MS\\607")
workDir <- getwd()
filePath = paste0(workDir,"/data")
# fileName <- list.files(path=filePath)

# mushroom <- read_delim(paste0(filePath,"/","mushroom.data" ))
# coloumName <- c(" ")

mushroom_meta <- read_delim(paste0(filePath,"/","atr.txt"),delim=".",col_names = FALSE)

# using the Name from above tible to set the header of the mushroom dataset
mushroom <- read_delim(paste0(filePath,"/","mushroom.data" ),delim = ",",col_names = trimws(mushroom_meta$X2))



# coloumName <- c(" ")


# mushroom <- read.delim(paste0(filePath,"/","mushroom.data" ),sep = ",")
str_split(trimws(mushroom_meta$X3[1]),",",simplify = TRUE)

for (n in  20:length(mushroom_meta$X3)){
  # print (str_split(trimws(mushroom_meta$X3[n]),",",simplify = TRUE))
  # tempVar <- paste0(trimws(mushroom_meta$X2[n]))
  print(paste0(trimws(mushroom_meta$X2[n])))
  assign("tempVar",str_split(trimws(mushroom_meta$X3[n]),",",simplify = TRUE))
   # tempVar <- paste0("`",trimws(mushroom_meta$X2[n]),"`")
  for ( j in 1:length(tempVar))
  {
    # print(eval(tempVar[j]))
    # str_split(tempVar[j],"=")
    # ddply(mushroom,.paste0("`",trimws(mushroom_meta$X2[n]),"`"),mutate,paste0("`",trimws(mushroom_meta$X2[n]),"`") =as.character(user[which(user$AGENT_ID_ECC==`Business Partner`),c(15)]))
    # 
    # mutate(mushroom,paste0("`",trimws(mushroom_meta$X2[n]),"`") = ifelse(paste0("`",trimws(mushroom_meta$X2[n]),"`") ==  str_split(tempVar[1],"=",simplify = TRUE)[2], "edible", "poisonous")) 
    #  print(tempVar[j])
#     
#     revalue(x, c(a = "A", c = "C")) 
# mapvalues(x, c("a", "c"), c("A", "C")) 
  }
}

head(mushroom)
mushroom <- mutate(mushroom,classes = ifelse(classes == "p", "poisonous", "edible"))

# Update Menaing in the Column
mushroom$`cap-shape`<- revalue(mushroom$`cap-shape`,c(b="bell",c="conical",x="convex",f="flat",
                                  k="knobbed",s="sunken"))




# Update Menaing in the Column
mushroom$`cap-surface` <- revalue(mushroom$`cap-surface`,c(f="fibrous",g="grooves",y="scaly",s="smooth"))


# Update Menaing in the Column
mushroom$`cap-color` <- revalue(mushroom$`cap-color`,c(n = "brown" ,b ="buff", c="cinnamon", g= "gray" ,r ="green",p ="pink" ,u= "purple" ,e="red", w ="white", y= "yellow"))



#getting the row from meta table for Cap-surface
trimws(mushroom_meta[which(trimws(mushroom_meta$X2)=="cap-surface"),3])
# Split data by comma 
str_split(trimws(mushroom_meta[which(trimws(mushroom_meta$X2)=="cap-surface"),3]),",")

#Array 
temp_str <- str_split(trimws(mushroom_meta[which(trimws(mushroom_meta$X2)=="cap-surface"),3]),",",simplify = TRUE)
tempLen <- length(temp_str)

replace(mushroom$`cap-surface`, c("f","g","y","s"), c("fibrous","grooves","scaly","smooth"))





head(mushroom)

# Data Subset
mushroom_edible <- subset(mushroom,select = c(1:5))

# NOT Using 

# mushroom_edible <- mushroom[which(mushroom$classes=="edible"),]
# 
# mushroom_edible <- ddply(mushroom,c("`cap-shape`","`cap-surface`"),summarise, Count_bruises = sum(as.integer(`bruises?`)))
# 
# count (mushroom,c("classes","`cap-shape`","`cap-surface`"))

# Not Using


glimpse(mushroom)
head(mushroom)
head(mushroom_meta )
mushroom_meta
```


## Tab Group Heading  {.tabset .tabset-fade .tabset-pills}
>Some Text 
*List 

### Sub Item 1


### Sub Item 2

You can insert graph here

### Sub Item 3 

You can insert table here

### Sub Item Group {.tabset .tabset-fade .tabset-pills}

Create More Tab inside

#### Sub Group Item 1 

#### Sub  Group Item 2

#### Sub group Item 2

